### 2024-03-13 Scripts/Appendix_scripts/Appendix_pre-reg_analyses.Rmd
finished appendices, and adjusted introductionb, methods. and results sections.

```{r UnidimensionalityExploratoryAnalysis, include = FALSE}
extracted_data_list <- list(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean, data_1.12.3.2_clean,data_2.12.1_clean, data_2.12.2_clean, data_2.12.3_clean, data_2.15_clean, data_2.20_clean, data_2.23_clean, data_3.2.1.1_clean, data_3.2.1.2_clean, data_3.7.1_clean, data_3.7.2_clean, data_3.8.2_clean, data_5.1.1_clean, data_5.1.2_clean, data_5.7_clean, data_5.9.1_clean)

@@

```{r Hypothesis6Associations, include = FALSE}
## Associations between the QMP categories
# associations are generated using a helper function available in the source_ 
# script. These associations correspond to the coefficients between replication
# and original article QMPs of the various QMP types, as estimated through a 
# beta regression.
# Associations between the QMP categories (original QMP coding) MOVE THIS ANALYSIS TO INITIAL CODING APPENDIX
Results_H6_between <- Associations_H6(data_h6)

@@

```
Table \@ref(tab:H6ExploratoryAssociationsRevisedTable) shows the beta-regression tests for each of the QMP category comparisons. The relations that are consistent are those between original article definition QMPs with replication selection and total QMPs, original article selection QMPs with replication total QMPs, and finally original article quantification QMPs with replication selection QMPs. All of these relations were positive across both coding protocols (see Appendix ???), illustrating that a greater QMP ratio of the specified type in an original article is associated with an increase in QMP ratio for the specific QMP type, or total QMP ratio in the replication protocol.

@@

A possibler explanation for these results could be that original articles have to provide a clear definition as well as details on the scale, in order for a replication to be able to justify selecting the measure. A replication may also be in general more dependent on the original article for information on the definition of the constructs and the choice of measurement, compared to a description of the Operationalisation, quantification, and any modifications. These former are features of a measurement, which while preferably similar in a replication to the original, can and should be reported in the replication protocol even if the original article does not contain the details on these features itself. However, these are just speculations as the results showed no clear relations between different QMP types across original and replication (see Figure \@ref(fig:Plot46RevisedDataCode)), the number of tests were many while multiple testing was not corrected for, and finally testing of causal links was not possible with this data.

>>>>

```{r UnidimensionalityExploratoryAnalysis}
extracted_data_list <- list(data_1.10_clean, data_1.11_clean, data_1.12.3.1_clean, data_1.12.3.2_clean,data_2.12.1_clean, data_2.12.2_clean, data_2.12.3_clean, data_2.15_clean, data_2.20_clean, data_2.23_clean, data_3.2.1.1_clean, data_3.2.1.2_clean, data_3.7.1_clean, data_3.7.2_clean, data_3.8.2_clean, data_5.1.1_clean, data_5.1.2_clean, data_5.7_clean, data_5.9.1_clean)

@@

```{r Hypothesis6Associations}
## Associations between the QMP categories
# associations are generated using a helper function available in the source_ 
# script. These associations correspond to the coefficients between replication
# and original article QMPs of the various QMP types, as estimated through a 
# beta regression.
# Associations between the QMP categories (original QMP coding) MOVE THIS ANALYSIS TO INITIAL CODING APPENDIX
Results_H6_between <- Associations_H6(data_h6)

@@

```
Table \@ref(tab:H6ExploratoryAssociationsRevisedTable) shows the beta-regression tests for each of the QMP category comparisons. The relations that are consistent are those between original article definition QMPs with replication selection and total QMPs, original article selection QMPs with replication total QMPs, and finally original article quantification QMPs with replication selection QMPs. All of these relations were positive across both coding protocols (see Appendix D), illustrating that a greater QMP ratio of the specified type in an original article is associated with an increase in QMP ratio for the specific QMP type, or total QMP ratio in the replication protocol.

@@

A possible explanation for these results could be that original articles have to provide a clear definition as well as details on the scale, in order for a replication to be able to justify selecting the measure. A replication may also be in general more dependent on the original article for information on the definition of the constructs and the choice of measurement, compared to a description of the Operationalisation, quantification, and any modifications. These former are features of a measurement, which while preferably similar in a replication to the original, can and should be reported in the replication protocol even if the original article does not contain the details on these features itself. However, these are just speculations as the results showed no clear relations between different QMP types across original and replication (see Figure \@ref(fig:Plot46RevisedDataCode)), the number of tests were many while multiple testing was not corrected for, and finally testing of causal links was not possible with this data.
